---
title: "Data Visualization"
author: "Ruitao Lin"
date: "10/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("gglpot2")
#install.packages("tidyverse")
#install.packages("dplyr")
library("tidyverse")
library("ggplot2")
library("tibble")
library("dplyr")


```

## The Dataset

The following dataset is about the fuel economy of some car models.
```{r mpg}
view(mpg)
```



## Some Plots for the Dataset
```{r manufacture, echo=FALSE}
ggplot(data = mpg) +
  geom_histogram(mapping = aes(x = year), binwidth = 0.5)
```

The histogram above shows the distribution of the year that the car is made. The dataset only includes car models at 1999 and 2008



```{r disp, echo=TRUE}
ggplot(data = mpg) +
  geom_histogram(mapping = aes(x = displ), binwidth = 0.1)
```

The plot above shows the distribution of engine displacement in liter. Most cars have displacement at 1.8 liters.

```{r}
mpg %>%
  ggplot(mapping = aes(x = displ, y = cty)) + 
    geom_point() + 
    geom_smooth(method = lm) +
    ggtitle("Fuel Economy and engine") + xlab("engine displacement") + ylab("fuel economy in city")
```

The graph above plots the relationship between engine displacement and fuel economy for each individual car. Now I will group the cars into manufacturer and replot the relationship.

```{r}
mpg %>%
  group_by(manufacturer) %>%
  summarise(mean_displ = mean(displ), mean_cty = mean(cty)) %>%
  ggplot(mapping = aes(x = mean_displ, y = mean_cty)) + 
    geom_point() + 
    geom_smooth(method = lm) +
    ggtitle("Fuel Economy and engine") + xlab("engine displacement") + ylab("fuel economy in city")
```

In general, the larger the engine displacement, the worse the car performs in city in terms of fuel economy.




  